decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-10 README.Rmd
order and leontief

@@

Source decomposition
---------------------------------------
 * Small derivation
 * R demonstration using WIOD data

We can now decompose the elements using the Source decomposition.
```{r source}
source <- kung_fu( elements )
```

```{r source-wrapper}
source2 <- decomp( x = intermediate_demand,
                   y = final_demand,
                   k = region_names,
                   i = industry_names,
                   o = output ,
                   method = "source"           )
```

```{r source-eval}
dim(source)
```

>>>>

Leontief decomposition
---------------------------------------
 * Small derivation
 * R demonstration using WIOD data

We can now decompose the elements using the Source decomposition.
```{r leontief}
leontief <- kung_fu( elements )
```

```{r leontief-wrapper}
leontief <- decomp( x = intermediate_demand,
                   y = final_demand,
                   k = region_names,
                   i = industry_names,
                   o = output ,
                   method = "source"           )
```

```{r source-eval}
dim(leontief)
```

@@
